% Setup
\graphicspath{./figures}

\chapter{Systems Survey and Analysis of State-of-the-Art}
\label{chap:survey}

% Introduction
% - What will this chapter contain and what resaarch question it tries to answer
% - Survey -> Identify existing SM Systems
% - Survey -> Deep dive into the individual systems
% - Result: Qualitative analysis on existing systems
Following a general introduction to concepts relevant to this thesis in \cref{chap:background}, in this chapter, we present a literature and systems survey on the state-of-the-art \gls{sm} systems. The goal of this chapter is to provide an answer to \ref{rq-1}, \textit{How to compare, and evaluate \gls{sm} systems?} To identify the existing systems and objectively compare these systems, we first conduct a systematic survey. By using a systematic process, the results as presented in this chapter can be reproduced by anyone who follows the steps as presented in our methodology. The survey is conducted in two phases. The goal of the first phase is to identify existing systems in the \gls{sm} landscape. After this, we survey the literature on these individual systems. The data obtained through this survey is then synthesized and used to create a framework which compares the properties and characteristics of these state-of-the-art \gls{sm} systems. Finally, we conclude this chapter by providing an extensive analysis on the obtained qualitative results, and produce an answer to the research question.

% Rest of the chapter is structured as follows
% - The need for these surveys (related work)
% - Methodology used for both surveys
% - Results of 
The remainder of this chapter is structured as follows. First, in \cref{sec:survey:introduction} we discuss the related work and identify the need for a systematic systems survey. Next, in \cref{sec:survey:objectives} we define the goals which we aim to achieve with the survey. After this, in \cref{sec:survey:methodology} we present and explain the methodology used to conduct this survey. Furthermore, in \cref{sec:survey:results} we present and discuss the obtained results. Subsequently, in \cref{sec:survey:analysis}, we analyse the data in detail and introduce a comparison framework for state-of-the-art \gls{sm} systems. Finally, in \cref{sec:survey:summary}, we summarize our work and establish an answer to research question \ref{rq-1}.



\input{3_systems_survey/sections/01_introduction}
\input{3_systems_survey/sections/02_objectives}
\input{3_systems_survey/sections/03_methodology}
\input{3_systems_survey/sections/04_results}
\input{3_systems_survey/sections/05_analysis}
\input{3_systems_survey/sections/06_summary}