% Setup
\graphicspath{./figures}

\chapter{Design and Implementation of a Service Mesh Benchmark}
\label{chap:system-design}

% Introduction
% - What will this chapter contain and what resaarch question it tries to answer

% Prev chapter -> General
% This chapter -> Performance oriented + importance
In the previous chapter (\cref{chap:survey}), we conducted a systems survey and identified several state-of-the-art \gls{sm} systems. We examined the architectural differences between these systems and compared them on domain-specific functional and non-functional requirements. We then discussed the theoretical performance implications of the architectural styles that we had identified. These performance implications have an effect on the performance of all software services in an environment and can cause a major bottleneck. With these concerns in mind, we dive deeper into the performance of \gls{sm} systems.


% Which RQ will we answer
% Related work -> Shortcomings
% What we do to solve these shortcomings
In this chapter, we provide an answer to research question \ref{rq-2}. \textit{How to design and implement a \gls{sm} benchmark which evaluates the performance of \gls{sm} systems?} During the systems survey, we observed that there was no relevant work found in the \gls{pl}. Furthermore, preliminary research has shown that previous and current efforts made to evaluate these performance characteristics are either in early stages or have limited functionality. To solve these shortcomings, we present a \gls{sm} benchmark instrument and implement a prototype that supports various workloads, application level protocols and \gls{sm} systems.

% Rest of the chapter is structured as follows
% - The need for these surveys (related work)
% - Methodology used for both surveys
% - Results of 
The remainder of this chapter is structured as follows. First, in \cref{sec:system:objectives} we introduce the goals of the benchmarking instrument. Second, in \cref{sec:system:sut} we describe the components that are part of the \gls{sut}. Afterwards, in \cref{sec:system:requirements-analysis} we present a requirement analysis in which we formalize the stakeholders, use cases and system requirements of the instrument. Next, in \cref{sec:system:design} we present the design of the benchmarking instrument. Following that, in \cref{sec:system:implementation} we discuss the implementation details of the system. Finally, in \cref{sec:system:analysis} we analyse the proposed design and implementation.

\input{4_system_design/sections/01_objectives}
\input{4_system_design/sections/02_system-under-test}
\input{4_system_design/sections/03_requirements-analysis}
\input{4_system_design/sections/04_design}
\input{4_system_design/sections/05_implementation}
\input{4_system_design/sections/06_analysis}
