% Setup
\graphicspath{./figures}

\chapter{Experimental Evaluation of Service Mesh systems}
\label{chap:experimental-evaluation}

% Introduction
% - What will this chapter contain and what resaarch question it tries to answer

% Prev chapter -> Design of the benchmark and implementation
% This chapter -> Design of experiments, conducting of experiments and results
In the previous chapter (\cref{chap:system-design}), we defined the \gls{sut} and the metrics that are important to evaluate the performance aspects of \gls{sm} systems. This ultimately led to the design, and implementation of \textit{Mesh Bench}, a benchmarking system for \gls{sm} systems. In this chapter, we present the experimental evaluation of \gls{sm} systems using the aforementioned benchmarking tool. With this, we provide an answer to research question \ref{rq-3}. \textit{What are the differences between the different \gls{sm} systems in terms of overhead, throughput and latency?} 


% Rest of the chapter is structured as follows
% - Experimental Setup
% - Experimental Results
% - Analysis/Discussion
The remainder of this chapter is structured as follows. First, in \cref{sec:experiments:design} we introduce the design of the experimental setup. After this, in \cref{sec:experiments:microbenchmarks} we evaluate  and measure the impact of our experimental environment and functional components of our benchmark through several micro benchmarks. Subsequently, in \cref{sec:experiments:results} we present the results of our experimental evaluation and perform an extensive analysis. After that, in \cref{sec:experiments:threats}, we discuss any threats to validity for our experimental evaluation. Finally, in \cref{sec:experiments:summary} we provide a summary of the contents discussed in this chapter.

\input{5_experimental_evaluation/sections/01_design}
\input{5_experimental_evaluation/sections/02_microbench}
\input{5_experimental_evaluation/sections/03_results}
\input{5_experimental_evaluation/sections/04_threats}
\input{5_experimental_evaluation/sections/05_summary}
